### 2018-01-17 project.tex
Redo Prop1
update on proof proposition 1

  \begin{definition}
    A topology is...
  \end{definition}

  \begin{theorem}
    An arbitrary intersetion of closed sets is closed.
  \end{theorem}

  \begin{proof}
    Because.
  \end{proof}

\end{document}

>>>>

  \begin{proposition}
      Any finite union of closed sets is closed, and any arbitrary intersection of closed sets is closed.
  \end{proposition}

  \begin{proof}
  	Proposition 1
  	\newline
	A, B $\in \tau \Rightarrow$ A $\cap$ B $\in \tau$ $\Rightarrow \overline{A \cap B} \not\in \tau$
	\newline
	$\overline{A \cap B} = \overline{A} \cup \overline{B}$
	\newline
	$\overline{A} \cup \overline{B} \not\in \tau$
	\newline \newline
	Also:
	\newline
	X = (a, z) $\in \tau$
	\newline
	A = (j, k) $\in$ X
	\newline
	$\overline{A}$ = (a, j] $\cup$ [k, z) $\not\in \tau$
	\newline \newline
	If $A \subseteq \tau$ then $\bigcup A \in \tau$
	\newline
	If $A$ contains at least one limit point $k$, we call this $\overline{A}$ if $\overline{A} \not\in A$, then $\overline{A} \not\in \tau$
	\newline
	If $\overline{A} \not\in \tau$, then $\overline{\bigcup A} \not\in \tau$
	\newline
	$\overline{\bigcup A} = \bigcap \overline{A} \not\in \tau$
  \end{proof}

	\begin{proposition}
		A set K in a topological space X is closed if and only if K contains all its limit points.
	\end{proposition}
	\begin{proof}
		Proposition 2 Part 1 - Prove if K contains all its limit points then that implies X$\setminus$K $\in \tau$

	\end{proof}
	\begin{proof}
	Proposition 2 Part 2 - Prove if X$\setminus$K $\in \tau$ then that implies that K contains all of its limit points.
		\newline
		Suppose $\exists K \in X$ and that $K$ contains all its limit points.
		\newline
		$\exists  x$ such that $x \in X \setminus K$. It follows that if $x \in X \setminus K$ then $x \not\in K \Rightarrow x \neq $ limit point $\in K$. $\therefore \exists \bigcup x'$ limit points $\in K$
	\end{proof}
\end{document}
